Particle Swarm Optimization for Crystallography

### 2009-02-26 crystallography/paper.tex
Started on honors thesis, added some other things.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results
\section{Results (Maybe Issues with Optimization?)}
\label{sec:results}
TODO.

@@

Work has been done on the use of particle swarm optimization in parallel with 
large numbers of particles \cite{mcnabb-gecco09}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Issues with Optimization
\section{Issues with Optimization}
\label{sec:issues}
TODO.

@@

The topology that was used in the PSO algorithm was the gbest topology.
Experiments were done with lbest to determine which was more efficient, and it
was discovered that for this problem gbest was better.  Averages over three
runs are shown in Figure (make figure) for the two topologies.

Work has been done showing that when running PSO in parallel with large swarms
more complicated topologies can do just as well as gbest while decreasing the
amount of communication required~\cite{mcnabb-gecco09}.  However, as the
function evaluation for this problem takes several minutes, the amount of
communication time for gbest is negligible when compared to the function
evaluation time.  The communication overhead for each iteration was discovered
to be about 8 seconds for the MRPSO implementation used.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results
\section{Results}
\label{sec:results}
TODO.
